Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-15 ms.tex

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig9.pdf}
\caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points). The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM. Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
\label{fig:tspec}
\end{figure}

>>>>

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
=======
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and find the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$\,s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig9.pdf}
\caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points). The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM, with squares indicating the model binned over the \Spitzer\ bandpasses. Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
\label{fig:tspec}
\end{figure}
